Network Trait marker for working memory deficit in Schizophrenia: a multi site study

### 2016-03-01 manuscript.tex
page
page margin

\documentclass[preprint,authoryear,review,12pt,times]{elsarticle}
%\documentclass[final,5p,times,twocolumn]{elsarticle}

@@

%%
%% Start line numbering here if you want
%%
% \linenumbers

@@

>>>>

\documentclass[preprint,authoryear,review,12pt,times]{elsarticle}
\usepackage{geometry}
\geometry{left=2.54cm,right=2.54cm,top=2.54cm,bottom=2.54cm}
%\documentclass[final,5p,times,twocolumn]{elsarticle}

@@

%%
%% Start line numbering here if you want
%%
\pagewiselinenumbers
\linenumbers

@@

\subsection*{Mega analyses}
As we considered, a single site imaging study may be biased by the scanner, imaging protocol, and clinical measures. To overcome these drawbacks, we acquired high quality fMRI data with common protocal across different sites from unique samples of schizophrenia patients with the same ethinic origin, as a potentially representative participant sample. The subjects are also recruited by the same critiria and the clinical scores are assessed by the stardards. Despite these control measures, the data and the statistical results may be influenced by the differences in psychopathology, exposuer to antipsoychotic medication andf the scanners used for iamge acquisitions across patients from different sites scanner type and some other potential effects. In order to assess the replication of the effects from the entire dataset within smaller subsets, Meta-analysis is used here to pooling resutls from single site and to increase the statistical power (J A. Turner, 2013, S G, Costafreda, 2009). To model/capture the heterogeneous induced by the different subjective recruitment strategies, cognitive paradigms, acquistion software and hardware, and the individial variance in coregistering to the template, we treat site factor as a random effect. By applying such multi-site experiment design and pooling stratergy, we were able to, first, reduce the possibility of biased results in a single site and provide a reliable and generalized results; second, extract novel insights from existing large-scale datasets by increasing the statistical power; thied ,the sample we collected is a representive righthanded Han chinese population which was collected from hospitals distributed across China.
